\chapter{Evaluation}
\label{chap:evaluation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experimental Design}

A number of experiments were ran to evaluate the correctness of this robot control system.

\subsection{Hardware Interaction}

These experiments were created to evaluate that the systems used to control the hardware used in the robot operated correctly.

Check one servo.

Check multiple servos.

Check ranges.

Check timings.

Video feeds from Xtion.

\subsection{Locomotion}

These experiments were created to evaluate that the systems designed to handle locomotion operated correctly.

Calibration tool.

Calibrated offsets applied.

Walk cycle (linear).

Walk cycle (rotation).

Walk cycle (combination). 

\subsection{Sensing}

These experiments were created to evaluate that the systems could interpret the world around the robot via the supplied sensory input.

Visual odometry (manual movement of camera).

Visual odometry (walk cycle).

Mapping (stationary).

Mapping (object in front).

Mapping (while walking).

\subsection{Navigation}

These experiments were created to evaluate that the systems could navigate autonomously using the interpreted sensory information.

Navigation accuracy. (no obstacles, straight line)

Navigation accuracy. (obstacle in way, curved path)

Obstacles in way during navigation.

\section{Results}

\subsection{Hardware Interaction}

Issues with timing, seems to be host dependent.

\subsection{Locomotion}

Difficulty in calibrating by eye alone. 

Servos are inaccurate with small changes.

Maximum speed constraints.

\subsection{Sensing}

Visual odometry drift. Difficulty with stationary rotation. Interesting reaction to mirrors. No resync if location is lost.

Mapping is awesome all of the time, ruined by visual odometry.

\subsection{Navigation}

It works alright, I guess.