\documentclass{l4proj}

\usepackage{alltt}
\usepackage{microtype}
\usepackage{textcomp}
\usepackage[small,bf]{caption}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{enumitem}
\usepackage{booktabs}

\usepackage[usenames, dvipsnames]{color}
\usepackage{listings}
\lstset{
	basicstyle=\ttfamily
}

\usepackage{graphicx}
\graphicspath{{./images/}}

\usepackage[]{hyperref}
\hypersetup{
    colorlinks = true,
    citecolor = black,
    linkcolor = black,
    urlcolor = black,
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title{Visual Control of a Hexapod Robot}
\author{Daniel Callander}
\date{March 28, 2014}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}
Robot control systems require a large underlying infrastructure of software to facilitate any complex behaviour. Typical systems require a means for communicating with hardware, locomotion control for movement, vision systems for guidance and environment mapping, autonomous navigation, means of user interaction, and so on. Each of these components requires a deep understanding of the subject matter and an immense number of person hours to design, implement, and test.

We implement a robot control system for a hexapod-type robot using the Robot Operating System (ROS) as a framework, an open-source framework designed specifically for building robot control systems. Through this implementation, we show that it is possible to endow a robot with these complex behaviours---specifically visual odometry, environment mapping and autonomous navigational functionalities---without the need to invest a large number of person hours. The key advantage of ROS is its vast amount of standard and community-provided packages which implement the necessary functionality for these complex behaviours. We make great use of these packages, offloading the complexities of development to those who are more qualified. 

Furthermore, we show that it is possible to implement these behaviours on a robot built using only consumer components rather than expensive research hardware. An RGB-D camera is used as the primary sensor for understanding the environment, which is used to provide mapping and positional information throughout the control system.
\end{abstract}

\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}
I would like to thank Dr. Paul Siebert for providing me with his invaluable guidance and expertise throughout the project. It would have been very tough going without his help! 

\noindent
I would also like to thank my fantastic friends and family for their support during the final stages of the project, especially for their proof-reading services for which I am extremely grateful.

\noindent
Finally, it would be rude of me not to thank the robot in some form for remaining (mostly) intact throughout the project. Even though the legs fell off a few times, everything remained working right to the very end.

--- Daniel Callander, 2014
\end{abstract}

\educationalconsent
\tableofcontents

\include{1_introduction} 
\include{2_background}
\include{3_approach}
\include{4_implementation}
\include{5_evaluation}
\include{7_conclusion}
\include{8_appendix}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\renewcommand{\bibname}{References}
\bibliographystyle{plain}
\bibliography{report}

\end{document}
